% status: 0
% chapter: TBD

\title{Performance benchmarks}

\author{Yue Guo}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{Smith Research Center}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47408}
  \country{USA}}
\email{yueguo@iu.edu}

\begin{abstract}
This project paper shows the proposal that needed in project, which 
provides the goal, the design, the scenarios and the expectations.
\end{abstract}

\keywords{Cassandra, MongoDB, hid-sp18-508}


\maketitle


\section{Introduction}
Cassandra and MongoDB are both not Relational DataBase Management System. 
There are four kinds of database, including Key-Value Stores, Big Tablle 
Clones, Document Database and Graph Database. Cassandra is a kind of Big 
Table Clones, while MongoDB is a kind of Document Database. Cassandra more 
focuses on Availability while MongoDB focuses more on Consistency. So there
 should be some difference in their performance when dealing with same data 
 and same operations on the same platform. After deploying both on the same 
 platform and testing same data on them, their performance can be compared. 
 ``Understanding the performance behavior of a NoSQL database like Apache 
 Cassandra? under various conditions is critical. Conducting a formal proof 
 of concept (POC) in the environment in which the database will run is the 
 best way to evaluate platforms~\cite{hid-sp18-508-benchmarking}. ''


\section{Design}
Choose MongoDb as backend first, then use Cassandra as backend. Use the adult
 data from UCI Machine Learning Repository to test. The performance metrics include: 

1. How fast can it process when using different backends

2. Endurance testing. Running search operation continuously to confirm its 
sustainability.

\section{Scenarios}

Using server connected to MongoDB:

1. Insert all data

2. Run search operation every second

3. 10 clients run search operation at the same time

4. 5 clients run search operation, 5 clients run delete operation at the same time

5. 5 clients run search operation, 5 clients run insert operation at the same time

6. 5 clients run insert operation, 5 clients run delete operation at the same time


Using server connected to Cassandra:

1. Insert all data

2. Run search operation every second

3. 10 clients run search operation at the same time

4. 5 clients run search operation, 5 clients run delete operation at the same time

5. 5 clients run search operation, 5 clients run insert operation at the same time

5. 5 clients run insert operation, 5 clients run delete operation at the same time


\section{Results}
What parameter:

use time [options] COMMAND [arguments], which can shows four kind of information:
 Time resources, Memory resources, IO resources and Command info.

How to process:

Redirect the output of time command into the specified file. And then write a 
program to analyze those outputs and do some statistics on those results. 


\section{Conclusion}
Compare the performance of MongoDB and Cassandra, especially the consistency 
and availability.

\begin{acks}

  The authors would like to thank Dr.~Gregor~von~Laszewski for his
  support and suggestions to write this paper.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 

